\documentclass[a4paper]{article}
\usepackage{datetime}

\author{Minute Taker: Xin Wang}
\title{Team Meeting 2}
\date{20 May 2020}

\begin{document}

\maketitle
\section{Attached Meeting Documents} 
All attached documents can be found within the same folder as meeting minutes.
\begin{itemize}
    \item Belbin roles questionnaire: \textit{BELBIN INVENTORY}
\end{itemize}

\maketitle
\section{Minutes} 
\subsection{Agenda 1: Team Roles}
\subsubsection{Discussion}
\begin{itemize}
    \item Discussed each team member's Belbin roles and decided which roles to take in the project.
    \item Rough timelines of the project are established.
    \item How to manage the team and the best form that applies to the team.
\end{itemize}
\subsubsection{Conclusion}
\begin{itemize}
    \item Belbin results and team roles to be added in the report.
    \item Waterfall team management approach felt best suited by the team.
    \item Gnatt chart to be created by Xin Wang.
\end{itemize}

\subsection{Agenda 2: Preliminary Research}
\subsubsection{Discussion}
\begin{itemize}
    \item Parser design is pretty standard so not much use in investigating it deeply.
    \item Should program use basic nodal analysis or modified nodal analysis.
\end{itemize}
\subsubsection{Conclusion}
\begin{itemize}
    \item Preliminary designs started to investigate nodal analysis and modified nodal analysis.
\end{itemize}


%Agreement and verification%


\vspace*{\fill}
\begin{center}
This document and all its attachments have been sent to and accepted by the following members of the team:
\begin{itemize}
\item Adam Rehman
\item Brandon Cann
\end{itemize}
\end{center}

\end{document}

