\documentclass[a4paper]{article}
\usepackage{datetime}

\author{Minute Taker: Xin Wang}
\title{Team Meeting 3}
\date{3 June 2020}

\begin{document}

\maketitle
\section{Attached Meeting Documents} 
All attached documents can be found within the same folder as meeting minutes. 
\maketitle
\section{Agenda 1: Xin's Repatriation Flight} 
\subsection{Discussion}
\begin{itemize}
    \item Xin Wang has been contacted by the South African Embassy of a repatriation flight
    from Germany. Current date has not been set but the embassy has notified 
    that it is in talks with the German government.
    \item There is no guarantee there would be WIFI within the mandatory government 
    quarantine facility. 
    \item Team has finished basic component support and the deadline is nearby.
\end{itemize}
\subsection{Conclusion}
\begin{itemize}
    \item The remaining two on the team agreed that they will continue on and work 
    on testing and advanced component support.
    \item Xin Wang will notify the professors when there is a definite date on the flight.
    \item The report will be prioritised by Xin Wang to ensure reports are finished.
\end{itemize}

\section{Agenda 2: Program Status} 
\subsection{Discussion}
\begin{itemize}
    \item Basic requirements of the program are completed. 
    \item Testing and advanced components are not completed yet.
\end{itemize}
\subsection{Conclusion}
\begin{itemize}
    \item Adam Rehman and Brandon Cann will handle testing, adding testing results and 
    researching into advanced components. 
    \item Xin Wang will finish report and look into Newton Raphson Iteration.
\end{itemize}


\vspace*{\fill}
\begin{center}
This document and all its attachments have been sent to and accepted by the following members of the team:
\begin{itemize}
\item Adam Rehman
\item Brandon Cann
\end{itemize}
\end{center}

\end{document}

